mintEMU Software Management Plan

### 2023-03-17 analysis/paper/paper.qmd

emu_theses$text_clean <- emu_theses$text |> 
  clean_basic() |> 
  str_remove_all(find_meta_stopwords(emu_theses) )  
```

```{r}
#| label: preview
#| include: false

# Preview theses in increasing order of graduation year
emu_theses %>% 
  arrange(graduation_year) %>% 
  pull(text_clean) %>% 
  head_text(head_n = 5)

# Show distribution of the length of theses
hist(str_length(emu_theses$text_clean))
```

@@

stop_words_custom <- emu_theses %>% 
  unnest_tokens(output = word, input = title) %>%   ### add words from the title
  select(word) %>% 
  rbind(., data.frame(word = c("preface", "foreword", "introduction", "conclusion", "thesis", 
                               "source", "author"))) %>% 
  # rbind(., data.frame(word = c("city", "urban", "urbanism"))) %>% 
  rbind(., data.frame(word = c("hab", "km")))

emu_theses_words <- emu_theses %>%
  mutate(author = paste(first_name, last_name)) %>% 
  select(author, title, text, -c(graduation_year, first_name, last_name)) %>% 
  unnest_tokens(output = word, input = text) %>%   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") %>%  # remove stop words
  anti_join(stop_words_custom, by = "word")
```

>>>>

emu_theses$text_clean <- emu_theses$text |>
  clean_basic()

```

@@

emu_theses$text_clean <- emu_theses$text_clean |>
  str_remove_all(find_meta_stopwords(emu_theses)) |> 
  str_remove_all(subject_stopwords()) |> 
  str_remove_all(document_stopwords())

emu_theses_words <- emu_theses |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>   # remove punctuation, convert to lowercase, separate all words
  anti_join(tidytext::stop_words, by = "word")
```

### 2023-03-17 analysis/smp.qmd

The research compendium will be documented as an R package, that is, all functions used in data processing and analysis will have associated documentation available from the help interface of R. Once loaded as a package all documentation is available to the user. The analysis will be fully documented in a Quarto computational notebook using R Markdown with the knitr engine.

@@

Installation requirements are described in the README file of the repository on GitHub:

@@

@@

@@

@@

**How do you plan to procure long term maintenance of your software?**

>>>>

The research compendium will be documented as an R package, that is, all functions used in data processing and analysis will have associated documentation available from the help interface of R. Once loaded as a package, all documentation is available to the user. The analysis will be fully documented in a Quarto computational notebook using R Markdown with the knitr engine.

@@

Installation requirements are described in the [README file](https://github.com/UD3-Lab/mintEMU#how-to-run-in-your-browser-or-download-and-run-locally) of the repository on GitHub.

@@

Citation guidelines are described in the [README file](https://github.com/UD3-Lab/mintEMU#how-to-cite) of the repository on GitHub.

@@

All the functions are well documented and the following R package structure so that they can be reused in other context. The repository README file has also a [Contributions](https://github.com/UD3-Lab/mintEMU#contributions) section, where [contributor guidelines](https://github.com/UD3-Lab/mintEMU/blob/main/CONTRIBUTING.md) and [Contributor code of Conduct](https://github.com/UD3-Lab/mintEMU/blob/main/CONDUCT.md) can be easily accessed.

@@

TBD

@@

The snapshot of the GitHub repository (e.g. release associated with the publication of the paper) will be published on Zenodo.

**How do you plan to procure long term maintenance of your software?**
The long-term maintenance of the software is not foreseen in the project.The software is making use of the package management software, `renv`, which help user retrieve the required version of dependencies needed to use the functionalities of the software.
